Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-24 ICLR25/experiments.tex
update table
update

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the utility function to select nodes to open, we focused on a small hard DNN, namely $5\times 100$, so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN. We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
To measure the accuracy, we measure the uncertainty of all nodes in a layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $n$ with bounds $[\alpha,\beta]$ is $unc(a) = \beta - \alpha$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$

@@

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|c|}
		\hline
		\text{Number $K$}  &  \bf Utility& Utility& \text{Strength} \cite{ DivideAndSlide} & \text{Random} &\text{Random}\\ \hline
		\hline
		0  &   1.761  && 1.761 & 1.761  &\\ \hline
		5  & \bf 1.532  && 1.704 &  1.729& \\ \hline
		10  & \bf 1.371  && 1.651 & 1.696 & \\ \hline
		15  & \bf 1.247  &&  1.599 &  1.653& \\ \hline
		20  & \bf 1.145  && 1.557 & 1.619 & \\ \hline
		25  & \bf 1.061  && 1.519 &  1.586 &\\ \hline
		30  & \bf 0.989  && 1.489 & 1.546 & \\ \hline
		35  & \bf 0.934  && 1.465 & 1.502 &\\ \hline
		40  & \bf 0.921 && 1.447 & 1.469 & \\ \hline
		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

@@

\subsection{Comparison with $\alpha,\beta$ Crown}

>>>>

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the utility function to select nodes to open, we focused on a small hard DNN, namely $5\times 100$, so as to obtain exact bounds for the first few layers using a full MILP encoding of the DNN. We tested over the $\vx=59$th image in the MNIST dataset, as it has a large number of unstable ReLU nodes in the first few layers ($61$ in the first and $55$ in the second layer), so we can experiment with a larger choice of values) for $K$.
To measure the accuracy, we measure the uncertainty of all nodes in a layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is $unc(a) = \UB - \LB$. The average uncertainty of layer $\ell$ is $\dfrac{\sum_{a\in l} unc(a)}{size(\ell)}.$

@@

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c|c|c|c|c|}
		\hline
		\text{Number $K$}  &  \bf Utility& Utility (1 layer)& \text{} \cite{ DivideAndSlide} & \text{Random} &\text{Random (1 layer)}\\ \hline
		\hline
		0  &   1.761  &1.761& 1.761 & 1.761  & 1.761\\ \hline
		5  & \bf 1.532  &1.603& 1.704 &  1.729&  1.729 \\ \hline
		10  & \bf 1.371  & 1.517& 1.651 & 1.696 & 1.701\\ \hline
		15  & \bf 1.247  &1.466&  1.599 &  1.653& 1.671\\ \hline
		20  & \bf 1.145  &1.438& 1.557 & 1.619 & 1.635\\ \hline
		25  & \bf 1.061  &1.427& 1.519 &  1.586 &1.601\\ \hline
		30  & \bf 0.989  &1.425& 1.489 & 1.546 & 1.574\\ \hline
		35  & \bf 0.934  &1.424& 1.465 & 1.502 &1.542\\ \hline
		40  & \bf 0.921 &1.424& 1.447 & 1.469 & 1.512\\ \hline
		116 (max) &  0.895 &1.424& 1.424 (max=$61$) & 0.895 &1.424  \\ \hline
	\end{tabular}
	\caption{Average uncertainty of $\MILP_X$ for nodes of the third layer, for $X$ with $K$ ReLU nodes of the 1st and 2nd layer (our utility function vs \cite{ DivideAndSlide} vs random choice).}
	\label{tab:example1}
	\vspace{-0.6cm}
\end{table}

@@

\subsection{Comparison with $\alpha,\beta$-Crown}
